---
title: "Individual Project 2"
author: "Mamon, Jasmin Mae G."
date: "2022-12-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r a}
library(twitteR) 
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(RColorBrewer)
library(tidytext)
library(rtweet)
library(tm)
library(slam)
library(wordcloud)
library(wordcloud2)
library(corpus)
```

>
Set-up credentials

```{r b}
CONSUMER_SECRET <- "WJXiTWYd6qY3NtwOaX8alreAbbv3sUpjiIVsMRYZWAL0j5xIAK"
CONSUMER_KEY <- "YULyHZwxMbIYGCmJEMSpvvv0D"
ACCESS_SECRET <- "HWJOiuSEVkzQTIGY9HZH14UTIRyHxRBv1wcLUt9ixHT9m"
ACCESS_TOKEN <- "1595205822350401536-hk8oSRVWz5LpnnM2fw0WRqbuwxk2zP"
``` 

>
Connect to twitter app

```{r c}
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```

>
Extract 10000 tweets from Twitter using twitteR package including tweets and retweets.

```{r d}
trends_on_twitter <- searchTwitter("Seventeen",
                             n = 10000,
                             lang = "en",
                             since = "2022-11-10",
                             until = "2022-12-4",
                             retryOnRateLimit = 120)

trends_on_twitter
```
 

>
Convert data into dataframe

```{r e}
trends_on_twitterDF <- twListToDF(trends_on_twitter)
trends_on_twitterDF


#Save is as a file
save(trends_on_twitterDF,file = "trendsonTweetsDF.Rdata")

#load the file
load(file = "trendsonTweetsDF.Rdata")

sapply_data <- sapply(trends_on_twitterDF, function(x) sum(is.na(x)))
sapply_data
```


>
2.Subset the retweets and the original tweets into a separate file.
SUBSETTING USING the dplyr() package

>
Original tweets

```{r f}
subTweets  <- trends_on_twitterDF %>%
  select(screenName, text, created, isRetweet) %>%
  filter(isRetweet == "FALSE")
subTweets
```

>
Saving a new file as Rdata

```{r g}
save(subTweets, file = "subTweetsDF.Rdata")
```

>
Grouping the date created

```{r h}
subTweets %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))
subTweets  %>% pull(created) %>% min()
subTweets %>% pull(created) %>% max()

crtd1 <- subTweets %>%  mutate(Created_At_Round = created %>%
                                 round(units = 'hours') %>% as.POSIXct())
crtd1
```

>
Plot on tweets by time using the library(plotly) and ggplot().

```{r I}
mams <- ggplot(crtd1, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "red", high = "blue")

mams %>% ggplotly()
```


>
With retweet

```{r j}
setTweets <- trends_on_twitterDF %>%
  select(screenName, text, created, isRetweet) %>%
  filter(isRetweet == "TRUE")
setTweets

#saving a new file as Rdata
save(setTweets, file = "setTweetsDF.Rdata")
```

>
Grouping the date created

```{r k}
setTweets %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))
setTweets  %>% pull(created) %>% min()
setTweets %>% pull(created) %>% max()

crtd <- setTweets %>%  mutate(Created_At_Round = created %>%
round(units = 'hours') %>% as.POSIXct())
crtd
```

>
Plot on tweets by time using the library(plotly) and ggplot().

```{r l}
mams2 <- ggplot(crtd, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "blue", high = "pink")

mams2 %>% ggplotly()
```



