---
title: "RWorksheet#5"
author: "Mamon, Jasmin Mae G."
date: "2022-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

**Worksheet for R Programming**

**Instructions:**

>
+ Use RStudio or the RStudio Cloud accomplish this worksheet.

>
+ Save the R script as RWorksheet_lastname#5.R. 

>
+ Create your own GitHub repository and push the R script as well as this pdf
worksheet to your own repo. Do not forget to comment your Git repo

>
Accomplish this worksheet by answering the questions being asked and writing the code manually.

>
1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.
Course Year 2019 - 2020
1st 80
2nd 75
3rd 70
4th 60

>
a. Plot the data using a bar graph. Write the codes and copy the result.

```{r a, echo=FALSE}
one <- c("1st", "2nd","3rd","4th")
two <- c(80,75,70,60)
barplot((two), 
        ylab = "2019-2020",
        xlab = "Course Year",
        names.arg = c("1st", "2nd","3rd","4th"))
```

>
b. Using the same table, label the barchart with

>
Title = ” Enrollment of BS Computer Science
horizontal axis = “Curriculum Year” and
vertical axis = “number of students”

```{r b, echo=FALSE}
one <- c("1st", "2nd","3rd","4th")
two <- c(80,75,70,60)
barplot((two), 
         main = "Enrollment of BS Computer Science",
         ylab = "number of students",
         xlab = "Curriculum Year",
        names.arg = c("1st", "2nd","3rd","4th"))
```

>
2. The monthly income of De Jesus family was spent on the following: 60% on Food, 10% on electricity, 5% for savings, and 25% for other miscellaneous expenses.

>
a. Create a table for the above scenario.
Write the codes and its result.

```{r c, echo=FALSE}
de <- c(60,10,5,25)
       barplot(de,names.arg = c("Food", "electricity", "savings","miscellaneous"))
```

>
b. Plot the data using a pie chart. Add labels, colors and legend.
Write the codes and its result.

```{r e, echo=FALSE}
de <- c(60,10,5,25)
de_jesus <- round(de/sum(de) * 100, 1)
de_jesus <- paste(de_jesus, "%", sep = "")
pie(de,col = rainbow(length(de)), labels = de_jesus, cex = 0.8)

legend(1.0,0.5, c("Food", "electricity", "savings","miscellaneous"),
       cex = 0.8, fill = rainbow((length(de_jesus))))
```

>
3. Open the mtcars dataset.
a. Create a simple histogram specifically for mpg (miles per gallon) variable.

```{r f, echo=FALSE}
cars <- data(mtcars)
cars 
```

>
Use $ to select the mpg only. Write the codes and its result.
>
b. Colored histogram with different number of bins.
>
hist(mtcars$mpg, breaks=12, col="red")
>
Note: breaks= controls the number of bins

```{r g, echo=FALSE}
mtcarsDF <- c(mtcars$mpg)
hist(mtcars$mpg, breaks= 12, col = "red")
```

>
c. Add a Normal Curve

```{r h, echo=FALSE}
x <- mtcars$mpg
h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon",
        main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)
```

>
Copy the result

>
4. Open the iris dataset. Create a subset for each species.
a. Write the codes and its result.

```{r i, echo=FALSE}
data("iris")

h <- subset(iris, Species == "setosa")
h

i <- subset(iris, Species == "virginica")
i

j <- subset(iris, Species == "versicolor")
j
```


>
b. Get the mean for every characteristics of each species using colMeans().
Write the codes and its result.
Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])

```{r j, echo=FALSE}
setosa <- colMeans(h[sapply(iris,is.numeric)])
setosa

virginica <- colMeans(i[sapply(iris,is.numeric)])
virginica

versicolor <- colMeans(j[sapply(iris,is.numeric)])
versicolor
```

>
c. Combine all species by using rbind()
The table should be look like this:

```{r k, echo=FALSE}
table1 <- rbind(setosa,versicolor,virginica)
table1
```

>
d. From the data in 4-c: Create the barplot().
Write the codes and its result.
The barplot should be like this.

```{r l, echo=FALSE}

barplot(table1, beside = TRUE,
        col = c("red", "green","blue"),
        ylab = "Mean Scores",
        xlab = "Characteristics",
       main = "Iris Data")
```
